An Accurate Model for SARS-CoV-2 Pooled RT-PCR Test Errors

### 2021-09-15 paper.tex
Hi Royal Society Open whatever. Screw you for wasting my evening just for creating a useless DOI for my code. Sincerely, Yair

\subsection*{Code Availability}
Code for this manuscript is available at
\url{https://github.com/yairdaon/errorates}.

@@

@@

%% Todos
%% add refs to dilution and paragraph in start
PCR pooling , or simultaneously testing multiple samples, for the
presence of SARS-CoV-2 is increasing in popularity. It is commonly
assumed that including more than a single infected sample in a pooled
test does not increase the probability of a positive outcome. We
challenge this assumption with experimental data. We then analyze the
probability of misidentifying an infected individual and show that it
increases when the prevalence of infection decreases. However, low
infection prevalence is exactly the condition when pooling is most
efficient. We therefore implore the cautious use of pooling.

Relative increase in Dorfman pooling false-negative rates
$\err{exact}$. Left: Colors represent $\err{exact}$, the relative
percentage increase in the scheme false-negative rates relative to the
single test false-negative rates equation \eqref{eq:erel}. Right:
colors represent the difference between $\err{common}$ and
$\err{exact}$. The infection prevalence $q$, is varied on the x-axis,
while the test sensitivity is varied on the y-axis. Pool size $N$, was
chosen according to $q$ as in \cite{DorfmanYuvalDor}. The left panel
shows that $\err{exact}$ is largest for low prevalence values $q$. The
difference between $\err{common}$ and $\err{exact}$ can be as large as
30\%, as seen in the right panel.

Relative increase in Dorfman pooling false-negative rates
$\err{exact}$. Left: Colors represent $\err{exact}$, the relative
percentage increase in the scheme false-negative rates relative to the
single test false-negative rates equation \eqref{eq:erel}. Right:
colors represent the difference between $\err{common}$ and
$\err{exact}$. The infection prevalence $q$, is varied on the x-axis,
while the test sensitivity is varied on the y-axis. Pool size $N$, was
chosen according to $q$ as in \cite{DorfmanYuvalDor}. The left panel
shows that $\err{exact}$ is largest for low prevalence values $q$. The
difference between $\err{common}$ and $\err{exact}$ can be as large as
30\%, as seen in the right panel.

Illustration of the revised probabilistic model. A pool contains
individuals $\{1,2,3\}$ with state $\theta=(1,1,0)$ (i.e., individuals
1 and 2 are infected). A negative pooled test ($\data=0$) occurs when
three detection paths fail: A false-negative occurs for individuals
$1$ and $2$, each with probability $(1-\sens)$.  Additionally, no
false-positive detection occurs, with probability $\spec$. Individual
$3$ is not infected and does not contribute to the probability of the
pooled test result.

>>>>

\subsection*{Code Availability}
Data and relevant code for this research work are stored in GitHub:
\url{https://github.com/yairdaon/errorates} and have been archived
within the Zenodo repository:
\url{https://doi.org/10.5281/zenodo.5510563} \cite{MyCode}.

@@

\bibitem{MyCode}
Yair Daon, \emph{yairdaon/errorates: Release for archiving}, 2021.

@@
